\chapter{Reason you applied for aid}

\section{Instructions and Tips}
This section requires a small paragraph (about 150 words) about \textbf{the reason}. Some ideas for this section include
\begin{itemize}
\item To enhance and extends your knowledge.
\item To learn what school doesn't taught.
\item Due to your current financial ability that you'd really need a support in tuition fees.
\end{itemize}
Also, your paragraph should be flexible to the course's content. For example, 
\begin{itemize}
\item application for a mathematics course should be "enhance your mathematics skill", rather than "level up your coding skill"
\item artificial intelligence-related courses would \textbf{not really} focusing on coding but more theoretically. Therefore "to extends my knowledge in the field of AI" would be a better choice than "to know how to program a nice AI".
\end{itemize}
It's also a brilliant idea to bring your previous-taken courses in Coursera to your application.

\section{Examples}
\subsection{\textit{Deep Learning specialization}, December 2022}
My name is Hoang-Quan Tran and I am a senior studying Computer Science in Vietnam, majoring in Natural Language Processing. There are few people who are passionate enough to consider Natural Language Processing as a career in our country. Since the University does not offer sufficient knowledge about this field, I must take external classes to gain more experience, and Coursera is a suitable place to do that. 

I completed my Natural Language Processing specialization earlier this year. The course has dramatically helped me understand how Deep Learning works and how it can be applied to various Natural Language Processing tasks. Now I want to gain more skills with Deep Learning, so I am taking this course. 

Due to my status as a student, I cannot afford many external courses. I am still dependent on my family's financial support while taking some other part-time jobs to pay my bills and rent. This financial aid will assist me with my current studies and financial situation.

\subsection{\textit{Mathematics for Machine Learning and Data Science Specialization}, 2023}
My name is Hoang-Quan Tran and I am a senior studying Computer Science in Vietnam, majoring in Deep Learning (specifically Natural Language Processing). During my first years as a freshman, mathematics was a sophisticated topic for me. Later when I run into Deep Learning, I realised my mathematics skills are not eligible and therefore I must take further mathematics courses.

I completed several Specializations on Coursera, including Natural Language Processing, Deep Learning, Machine Learning and GANs. These courses were excellent, not just by their content and practical exercises but their awesome instructors who guided me through the process. Their teaching skills are so great, that I think Coursera is a great place to gain more knowledge in any field, including mathematics.

Due to my status as a student, I cannot afford many external courses. I am still dependent on my family's financial support while taking some other part-time jobs to pay my bills and rent. This financial aid will assist me with my current studies and financial situation.