\documentclass{article}

\usepackage[bottom]{footmisc}
\usepackage{fancyhdr}
\usepackage[colorlinks = true,
            linkcolor  = blue,
            urlcolor   = blue]{hyperref}
\usepackage{lastpage}
\usepackage{titlesec}
\usepackage{titling}
\usepackage[margin=1in]{geometry}

\pagestyle{fancy}
\lhead{\LaTeX\space by Quan, Tran Hoang}
\rhead{Quan, Tran Hoang's R\'esum\'e, updated \today}
\cfoot{Page \thepage\ of \pageref{LastPage}}

% Styles for the title
\renewcommand{\maketitle}{
    \begin{center}
        % Author's name
        {\huge\bfseries\theauthor}
        \linebreak\linebreak
        \itshape{R\'esum\'e}
    \end{center}
}

\begin{document}
    \author{Quan, Tran Hoang}
    \maketitle

    \section{Basic Informations}
        {\bfseries Quan, Tran Hoang} {\itshape{(his name is {\bfseries{Quan}}, family name {\bfseries{Tran}}, middle name {\bfseries{Hoang}})}}.
        \begin{itemize}
            \item {\bfseries{Born}}: \\
                November 22, 2001
            \item {\bfseries{Hometown}}: \\
                Ben Tre Town (today Ben Tre City), Ben Tre Province, The Socialist Republic of Vietnam.
            \item {\bfseries{Currently}}: \\
                Computer Science student @ VNUHCM - University of Science, Ho Chi Minh City, The Socialist Republic of Vietnam.
            \item {\bfseries{Languages}}: \\
                Vietnamese as mother tongue, can speak English well and some Russian.
            \item {\bfseries{Hobbies}}: \\
                Coding, writing, walking and sometimes gaming too.
        \end{itemize}

    \section{Technical Skills}
        % Language section
        \subsection{Language}
            \begin{itemize}
                \item Programming: C, C++.
                \item Scripting: Python, PHP, JavaScript, AutoIt.
                \item Markup: \LaTeX, Markdown, HTML, CSS.
            \end{itemize}

        % VCS (Version Control System)
        \subsection{Version Control System (VCS)}
            \begin{itemize}
                \item Using Git to deploys projects on GitHub.
            \end{itemize}

        % Using Office tools
        \subsection{Office tools}
            \begin{itemize}
                \item Using Microsoft Word in Advanced (MOS 832 points) and other Microsoft Office services in Basic.
                \item Using Google services (Google Docs, Google Sheets, Google Presentation,..) in Advanced.
            \end{itemize}

        % Operation Systems
        \subsection{Operating systems}
            \begin{itemize}
                \item Windows.
                \item Linux (Ubuntu).
            \end{itemize}

        % Image Editing section
        \subsection{Image Editing}
            \begin{itemize}
                \item Image editing with Adobe Photoshop CS3, Basic.
            \end{itemize}

    \section{Education}
        % Academic Timeline section
        \subsection{Academic Timeline}
            \begin{itemize}
                \item {\bfseries{2007 - 2019}}:
                attended primary\footnote{Ben Tre Primary School, from 2007 to 2012}, secondary\footnote{Ben Tre Secondary School, from 2012 to 2016} and high school\footnote{Nguyen Dinh Chieu High School, from 2016 to 2019} in Ben Tre.
                \item {\bfseries{2019 - now}}: Computer Science student at VNUHCM - University of Science\footnote{Faculty of Information Technology, VNUHCM - University of Science (fit@hcmus)}.
            \end{itemize}

        % Coding Timeline section
        \subsection{Coding Timeline}
            \begin{itemize}
                \item {\bfseries{June 2015}}: \\
                    started programming with AutoIt.

                \item {\bfseries{July 2015}}: \\
                    started programming with PHP and JavaScript.

                \item {\itshape{{\bfseries{2015 - 2018}}: \\
                    participated in some PHP projects, focused on improving PHP skills.}}

                \item {\bfseries{November 2016}}: \\
                    join the Nguyen Dinh Chieu High School Computer Science team.

                \item {\bfseries{February 2018}}: \\
                    participated in Ben Tre Province Competition in Computer Science for High School students\footnote{Vietnamese: Ky thi Hoc sinh gioi cap Tinh mon Tin hoc danh cho hoc sinh Trung hoc Pho thong tinh Ben Tre. This is a competitive programming contest, focus on implementing algorithms to solve problems.}, 2018.

                \item {\bfseries{June 2018}}: \\
                    started learning advanced PHP with Laravel framework.

                \item {\bfseries{October 2018}}: \\
                    started learning C/C++.

                \item {\bfseries{February 2019}}: \\
                    participated in Ben Tre Province Competition in Computer Science for High School students, 2019.

                \item {\bfseries{September 2019}}: \\
                    started programming with Python.
            \end{itemize}

        % Award section
        \subsection{Awards (during academic years)}
            \begin{itemize}
                \item {\bfseries{Consolation Prize}}, Ben Tre Province Competition in Computer Science for High School students, 2018 using Pascal.
                \item {\bfseries{III (third) Prize}}, Ben Tre Province Competition in Computer Science for High School students, 2019 using C/C++.
                \item {\bfseries{Contestant}} at the Microsoft Office Specialist World Championship Vietnam 2019 - Southern Elimination Round, with 832 points.
            \end{itemize}

        % Product section
        \subsection{Products I've made}
            \begin{enumerate}
                \item \href{https://github.com/trhgquan/Fororum}{Fororum - a forum made from Laravel with love and keyboard.}
                \item \href{https://github.com/trhgquan/JBomb}{JBomb - a Minesweeper-like game created with VanillaJS (pure JavaScript) and HTML5 Canvas.}
                \item \href{https://github.com/trhgquan/CPP}{Competitive Programming Practice.}
            \end{enumerate}

    % Contact section
    \section{Contacts}
        Send Quan an email:
        \begin{quote}
            \itshape{contacts (at) tranhoangquan (dot) codes}
        \end{quote}
        Visit him at his website:
        \begin{quote}
            \href{https://www.tranhoangquan.codes}{www.tranhoangquan.codes}
        \end{quote}
        His personal GitHub profile:
        \begin{quote}
            \href{https://github.com/trhgquan}{@trhgquan}
        \end{quote}
\end{document}